Titeln på avhandlingens språk

### 2023-04-24 body/part1/chapter1-introduction/background.tex
images

\gls{VR}, on the other hand, takes it a step further and involves forgoing the real world, completely immersing the user in a fully virtual environment~\cite{doerner2022virtual}.
Due to its deeply immersive nature, \gls{VR} requires users to wear specialized equipment such as a \gls{VR} headset.
The headset contains two high-resolution displays (one for each eye) and a set of headphones, and is connected to a computer or a gaming console, which generates the virtual environment in real-time.
The headset tracks the user's head movements and adjusts the virtual displays accordingly to create the illusion of being in a completely immersed in a different world.
Objects in the virtual environment can be interacted with either through the use of special hardware such as instrumented gloves or controllers, or by using sensors which track the user's hands.
Some advanced \gls{VR} platforms even include omnidirectional treadmills which allow the users navigate the virtual world by walking, running, and even jumping.

>>>>

\gls{VR}, on the other hand, takes it a step further and involves forgoing the real world, completely immersing the user in a fully virtual environment~\cite{doerner2022virtual}.
Due to its deeply immersive nature, \gls{VR} requires users to wear specialized equipment such as a \gls{VR} headset, as showcased in \cref{fig:vrheadset}.
The headset contains two high-resolution displays (one for each eye) and a set of headphones, and is connected to a computer or a gaming console, which generates the virtual environment in real-time.
The headset tracks the user's head movements and adjusts the virtual displays accordingly to create the illusion of being in a completely immersed in a different world.
Objects in the virtual environment can be interacted with either through the use of special hardware such as instrumented gloves or controllers, or by using sensors which track the user's hands.
Some advanced \gls{VR} platforms even include omnidirectional treadmills which allow the users navigate the virtual world by walking, running, and even jumping.

\begin{figure}
    \centering
    \includegraphics[height=26em]{figures/girl_VR}
    \caption[{ }]{
        A young user wearing a \gls{VR} headset.
        The headset completely encases the user's eyes and ears, providing a fully immersive virtual experience.\\

        {
            \footnotesize%
            Image by Miki Yoshihito on Flickr~\cite{picture:VRheadset}.
            Licensed under a \gls{CCBY} license.
        }
    }\label{fig:vrheadset}
\end{figure}
